Article 5 : Possible new treatment strategy for lung cancer

### 2019-12-14 _posts/2019-12-14-article-5/article-5.Rmd
modif. article 5

---
title: "Article 5 : Possible new treatment strategy for lung cancer"
author:
  - name: Aurélie Pinchart
date: 12-14-2019
output:
  distill::distill_article:
    self_contained: false
---

>>>>

---
title: "Article 5 : Possible new treatment strategy for lung cancer"
author:
  - name: Aurélie Pinchart
date: 12-14-2019
categories:
  - KRAS
  - MEK kinase
output:
  distill::distill_article:
    self_contained: false
---
